How Do Models Fail? A Visual Exploration Tool for Analyzing and Interpreting Natural Language Inference

### 2018-03-19 paper/background.tex
updates on background, intro (very minor change), and bib

\begin{itemize}
    \item Motivation for TE: reading comprehension, similarity of senten ce
    \item what is it?
    \item its connection with other NLP tasks (one of the key)
    \item
\end{itemize}

The grand challenge in natural language processing (NLP) such as
machine reading require a deeper understanding the

@@

The discrete nature of words and sentences presents additional challenge for
interpreting the model, since many visualization technique often employed
for images rely on continues nature of the input space (e.g., one can interpolate
real values much easier than interplolate between words/sentences).
%

% \subsection{Natural Language Inference}

@@

Textual entailment is one of major natural language tasks, namely translation, summarization, question

% \subsection{Interprebilty Challenges}

The introduction of attention mechanism~\cite{} allow simpler models to match or even outperform more complex / deeper models by exploiting the alignment of bits of local text between sentences. The new challenges

Making sense and explaining predictions made by deep neural networks is not only essential for validating and improving the model, but also becoming a necessity with increasing demands for model accountability (e.g., what is the evidence for making the decision) and model fairness (e.g., is the prediction affected by the bias in the training data).

>>>>

\begin{itemize}
    \item Motivation for : reading comprehension, similarity of sentennce
    \item what is it?
    \item its connection with other NLP tasks (one of the key)
    \item
\end{itemize}

The grand challenge in Natural Language Processing (NLP) is to have machine to acquire
deep comprehension of textual information. Major tasks include Natural Language Inference,
Machine Translation, Questions Answering, Summarization, and etc. 
Recently, neural networks models have performed strongly on these tasks.

Therefore, making sense and explaining predictions made by deep neural networks is not only 
essential for validating and improving the model, but also becoming a necessity with 
increasing demands for model accountability (e.g., what is the evidence for making the decision) 
and model fairness (e.g., is the prediction affected by the bias in the training data).

@@

%

\subsection{Interprebilty Challenges}

Compared with Conputer Vision, the discrete nature of words and sentences 
presents additional challenge for
interpreting the model, since many visualization technique often employed
for images rely on continuous nature of the input space (e.g., one can interpolate
real values much easier than interplolate between words/sentences).

On the other hand, a majority of recent NLP neural networks share the nature of 
end-to-end model, where the entire model operates as a black-box that takes 
vectorized input and yields final prediction for a specific task.
Therefore, to study the inside of end-to-end neural models, it is important to 
explore the interaction between intermediate representations and predictions.

The introduction of attention mechanism~\cite{bahdanau2014neural} allows 
pairwise interaction between hidden states. This interaction can be naturally explained
as a form of alignment which exposes an interpretable layer in end-to-end neural networks. 
Recently attention has contributed to many strongly-performed NLP models
~\cite{parikh2016emnlp},~\cite{rush2015neural},~\cite{yang2016hierarchical},
~\cite{seo2016bidirectional},~\cite{schwartz2017high}. 
We will focus on its application in Natural Language Inference task as proposed in~\cite{parikh2016emnlp}.
However notice that our visualization can be generalized to other attention models as well.

% The introduction of attention mechanism~\cite{} allow simpler models to match or even outperform more complex / deeper models by exploiting the alignment of bits of local text between sentences. The new challenges

\subsection{Natural Language Inference}
Natural Language Inference(cite?) is an important machine understanding task in NLP. 
The problem definition is to classify the relationship between a premise sentence and a hypothesis sentence. 
The prediction must fall in one of three catergories: $\{Entailment, Contradiction, Neutral\}$. 
$Entailment$ refers to that the textual information of hypothesis is embedded in premise; 
$Contradiction$ means the textuals of hypothesis opposes that of premise; 
and $Neutral$ implies no conclusion can be made on either $Entailment$ or $Contradiction$.

Recently ~\cite{BowmanAngeliPotts2015} proposed a large dataset for this task. We will examine 
the decomposable attention model~\cite{parikh2016emnlp} on this dataset with perturbation.

% showing an example??

@@

### 2018-03-19 paper/intro.tex
minor update to text
adjust evaluation panel size
fix toggle buttons
updates on background, intro (very minor change), and bib

Making sense and explaining predictions made by neural networks is also becoming a necessity with increasing demands for model accountability (e.g., what is the evidence for making the decision) and model fairness (e.g., is the prediction affected by the bias in the training data).
%
Due to these demands, many works have been dedicated to providing intuitive explanations for a given prediction. Such a system often approach the problem from a model agnostic approach that made them applicable to different applications (i.e., by fitting a simplier linear model near the prediction of interests).
%
However, despite being invaluable for the prediction interpretation task these methods often cannot adequately address the challenge in the model diagnostic process. More importantly, due to the model agnostic nature, they lack of the ability to access and explore the internal states of the model, which is vitally important to make sense of why a model fail.

In this work, we introduce a visualization system that through a tight yet flexible integration between visual analytic elements and the underlying model, allow a user to interrogate the model by perturbing the input, the internal state, as well as prediction while observing changes in other parts of the pipeline.
We use textual entailment task~\cite{BowmanAngeliPotts2015} as an example to illustrate how this system help natural language processing (NLP) researchers quickly identify the potential limitation of an NLP model, probe the inner states of the model for interpreting key mechanism such as attention, and ultimately come up with hypothesis on why the model fails.

>>>>

%%%%%%%%% accessing internal states are important %%%%%%%%%%%%
Making sense and explaining predictions made by neural networks is also becoming a necessity with increasing demands for model accountability (e.g., what is the evidence for making the decision) and model fairness (e.g., is the prediction affected by the bias in the training data).
%
Due to these demands, many works have been dedicated to providing intuitive explanations for a given prediction. Such a system often approach the problem from a model agnostic approach that made them applicable to different applications (i.e., by fitting a simplier linear model near the prediction of interests).
%
However, despite being invaluable for the prediction interpretation task these methods often cannot adequately address the challenge in the model diagnostic process. More importantly, due to the model agnostic nature, they lack of the ability to access and explore the internal states of the model, which is vitally important to make sense of why a model fail.

%%%%%%%%%% interrogate relationship between different componenet, modified different componenets %%%%%%%%%%%
Beside looking into the internal states, understanding how each of the component interact with each other provide more insight about the mechanism of the model.

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{pipeline}
 \caption{Language Inference Model Pipeline.}
\label{fig:projTransition}
\vspace{-5mm}
\end{figure}

In this work, we introduce a visualization system that through a tight yet flexible integration between visual analytic elements and the underlying model, allow a user to interrogate the model by perturbing the input, the internal state, as well as prediction while observing changes in other parts of the pipeline.
We use natural language inference task~\cite{BowmanAngeliPotts2015} as an example to illustrate how this system help natural language processing (NLP) researchers quickly identify the potential limitation of an NLP model, probe the inner states of the model for interpreting key mechanism such as attention, and ultimately come up with hypothesis on why the model fails.
